Analyzing the Factors Influencing Outbreak Duration in Toronto Healthcare Institutions

### 2024-11-27 paper/paper.qmd
update readme

---
title: "Understanding the Factors Influencing Outbreak Duration in Toronto Healthcare Institutions"
subtitle: "My subtitle if needed"
author: 
  - Kevin Cai
thanks: "Code and data are available at: [https://github.com/kevicai/toronto-healthcare-outbreak-prediction](https://github.com/kevicai/toronto-healthcare-outbreak-prediction)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Analyzing the Factors Influencing Outbreak Duration in Toronto Healthcare Institutions"
subtitle: "My subtitle if needed"
author: 
  - Kevin Cai
thanks: "Code and data are available at: [https://github.com/kevicai/toronto-healthcare-outbreak-prediction](https://github.com/kevicai/toronto-healthcare-outbreak-prediction)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---
